Testing the Relationship between Phenomenological Control related to Illusion Sensitivity

### 2025-03-18 paper/R1/manuscript.qmd
minor

::: {#tbl-table1}
```{r}
question <- c("Question","Hypothesis","Sampling Plan","Analysis Plan","Rationale for Deciding the Sensitivity of the Test","Interpretation Given Different Outcomes","Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity?", "Replicating findings from Lush et al., 2022 paper, we expect evidence of favour of an absence of relationship between VI and PCS", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations between the PC score and the VI performance for the 3 illusion types (corresponding to the error rate) will be computed using the *BayesFactor::BFCorrelation()* function (with the r-scale prior parameter set to ‘medium’)", "Evidence against a relationship between PC and VI will be found if BF10 <= 1/3, following the Lush et al., 2022 findings. BF10 > 3 will be interpreted as evidence for a relationship between these two measures.", "The hypothesis that VI sensitivity is independent from PC.", "The cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC.")

@@

## study design table
study_design_table <- flextable::flextable(study_design_df)
study_design_table <- set_table_properties(study_design_table, width = 1, layout = "autofit")
study_design_table <- set_caption(study_design_table, caption = "Study Design Table")
study_design_table <- delete_part(x = study_design_table, part = "header")
study_design_table <- bold(study_design_table, j = "question", bold = TRUE, part = "body")
study_design_table <- theme_apa(study_design_table)

@@

@@

::: {#fig-figure1}

![The parametric framework for visual illusions (Makowski et al., 2021) applied to the Müller-Lyer illusion (above). Below are examples of stimuli showcasing the manipulation of two parameters, task difficulty and illusion strength.](img/example_stimuli.png)

The parametric framework for visual illusions (Makowski et al., 2021) applied to the Müller-Lyer illusion (above). Below are examples of stimuli showcasing the manipulation of two parameters, task difficulty and illusion strength.
:::

::: {#tbl-table2}

![Illusions Task Example Stimuli.](img/illusion_table.png)

Illusions Task Example Stimuli.
:::

@@

The PCS will contain several manipulation check indices to identify problematic participants. **The phenomenological control task consists of various auditory and visual exercises. In one such exercise, participants receive the following instruction: “Open your eyes. You will see only two balls on the screen…just two balls”. However, three differently coloured balls are actually displayed. If participants select the option "no balls were shown", it indicates they failed to pay attention to both the auditory instructions and the visual stimuli. In another exercise, participants are asked to press the spacebar six times. If they press it fewer than five times within the allotted time, it suggests a lack of attentiveness to the auditory instructions. Participants will be excluded if they fail at least one of the attention checks.**

>>>>

::: {#tbl-table1}
```{r}
#| tbl-cap: "Study Design Table"

question <- c("Question", "Hypothesis", "Sampling Plan", "Analysis Plan", "Rationale for Deciding the Sensitivity of the Test", "Interpretation Given Different Outcomes", "Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity?", "Replicating findings from Lush et al., 2022 paper, we expect evidence of favour of an absence of relationship between VI and PCS", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations between the PC score and the VI performance for the 3 illusion types (corresponding to the error rate) will be computed using the BayesFactor::BFCorrelation() function (with the r-scale prior parameter set to ‘medium’)", "Evidence against a relationship between PC and VI will be found if BF10 <= 1/3, following the Lush et al., 2022 findings. BF10 > 3 will be interpreted as evidence for a relationship between these two measures.", "The hypothesis that VI sensitivity is independent from PC.", "The cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC.")

@@

## study design table
study_design_table <- flextable::flextable(study_design_df)
study_design_table <- set_table_properties(study_design_table, width = 1, layout = "autofit")
# study_design_table <- set_caption(study_design_table, caption = "Study Design Table")
study_design_table <- delete_part(x = study_design_table, part = "header")
study_design_table <- bold(study_design_table, j = "question", bold = TRUE, part = "body")
study_design_table <- theme_apa(study_design_table)

@@

```{r}
#| warning: false
#| label: "fig-illusion_framework"
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The parametric framework for visual illusions (Makowski et al., 2021) applied to the Müller-Lyer illusion (above). Below are examples of stimuli showcasing the manipulation of two parameters, task difficulty and illusion strength."

knitr::include_graphics("img/example_stimuli.png")
```

@@

```{r}
#| warning: false
#| label: "fig-illusionexample"
#| apa-twocolumn: false  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"
#| fig-cap: "The study involved three visual illusions, in which participants were instructed to respond as quickly as possible without making errors. Each illusion included two manipulated parameters: strength (e.g., the angle of the outward- or inward-pointing arrow-like fins in the Müller-Lyer illusion) and difficulty (e.g., the difference in line lengths in the Müller-Lyer illusion."

knitr::include_graphics("img/IllusionTable.jpg")
```

@@

The PCS will contain several manipulation check indices to identify problematic participants. **The phenomenological control task consists of various auditory and visual exercises. In one such exercise, participants receive the following instruction: “Open your eyes. You will see only two balls on the screen…just two balls”. However, three differently coloured balls are actually displayed. If participants select the option "no balls were shown", it indicates they failed to pay attention to both the auditory instructions and the visual stimuli. In another exercise, participants are asked to press the spacebar six times. If they press it fewer than five times within the allotted time, it suggests a lack of attentiveness to the auditory instructions. Participants will be excluded if they fail at least one of these checks. Participants will be excluded if they fail at least one of the attention checks.**
